---
title: Semantic Analysis
subtitle: Ayush Noori
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    toc: yes
editor_options: 
  chunk_output_type: inline
---

# Dependencies

Load requisite packages and define directories. Note that this script loads my personal utilities package, `ayushnoori/brainstorm`, which is available via GitHub.

```{r load-packages, message=FALSE, warning=FALSE}

# data manipulation
library(data.table)
library(purrr)
library(magrittr)
library(stringr)

# structural topic modeling
library(stm)

# data visualization
library(ggplot2)

# source utilities script
library(brainstorm)

```

Directories are relative to the R project path.

```{r define-directores}

ddir = file.path("Results", "2 - Parse Tweets")
rdir = file.path("Results", "3 - Semantic Analysis")

```

# Read Data

```{r read-data}

twt = readRDS(file.path(ddir, "Final Parsed Tweets.RDS"))

```

# Structural Topic Modeling

Read data using `stm::textProcessor()`, which is a wrapper around the `tm` package for text mining. For more details, please see the documentation [here](http://structuraltopicmodel.com).

```{r process-text}

# process text
processed = textProcessor(twt$CleanText, metadata = as.data.frame(twt))
# saveRDS(processed, file.path(rdir, "Processed Text.RDS"))
# plotRemoved(processed$documents, lower.thresh = seq(1, 200, by = 100))

# prepare documents
out = prepDocuments(processed$documents, processed$vocab, processed$meta)
# saveRDS(out, file.path(rdir, "Prepared Documents.RDS"))
out = readRDS(file.path(rdir, "Prepared Documents.RDS"))

# Removing 333045 of 451964 terms (333045 of 7150863 tokens) due to frequency 
# Removing 770 Documents with No Words 
# Your corpus now has 510174 documents, 118919 terms and 6817818 tokens.

```

Now, estimate a structural topic model using semi-collapsed variational EM. Since the initialization method is `Spectral`, we set the number of topics `K` to be `0` to use the algorithm of Lee and Mimno (2014) to estimate the number of topics.

```{r estimate-stm}

# stm_fit = stm(documents = out$documents, vocab = out$vocab, data = out$meta,
#               K = 0, init.type="Spectral", seed = 1234, max.em.its = 100)

stm_fit = stm(documents = out$documents, vocab = out$vocab, data = out$meta,
              K = 10, init.type="Spectral", seed = 1234, max.em.its = 100)

saveRDS(stm_fit, file.path(rdir, "Structural Topic Model K10.RDS"))

```

Visualize interesting topics.

```{r explore-topics}

sel_topics = c(1, 3, 5, 6, 9, 11, 14, 21, 23, 32, 34, 41)


```
