---
title: "COVID-19 Tweets"
subtitle: Ayush Noori
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme:
      bootswatch: minty
      primary: "#9AC1AE"
      navbar-bg: "#9AC1AE"
    social: menu
    source_code: embed
---


```{r global, include = FALSE}

# load flexdashboard library
library(flexdashboard)
library(bslib)

# load data in global chunk so it can be shared by all users of the dashboard
library(data.table)
library(purrr)
library(magrittr)
library(ggplot2)

# read .RDS object
twt = readRDS("Final Parsed Tweets.RDS")

```


Sidebar {.sidebar}
=====================================

Our project aims to characterize the public opinion of the COVID-19 pandemic by applying machine learning on COVID-related tweets. Rather than access the Twitter COVID-19 streaming endpoint directly, we use the pre-curated [USC JIMR Dataset](https://publichealth.jmir.org/2020/2/e19273/#ref24). After tweet hydration, we use natural language processing tools to derive aggregate features from our dataset.


```{r select-input}


```


Page #1
=====================================

Row
-----------------------------------------------------------------------

### Value Box {.value-box}

```{r value-box}

valueBox(value = nrow(twt), icon = "fa-twitter", color = "#F4D5A4",
           href = "https://www.twitter.com")

```

Row
-----------------------------------------------------------------------

### Template

```{r template}

